TBD

### 2020-11-02 outputs/paper/paper.Rmd
results updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lme4)
library(rstanarm)
library(brms)
```

@@

```{r}
mod <- glmer(binary ~ age_group + (1|education_grouped) + race_ethnicity + household_income_grouped,
           data = clean_survey_2,
           family = binomial()
           )

summary(mod)
```

### Summary Table
\begin{center}
\captionof{table}{3329}
\begin{tabular}{|l|l|l|l|}
\hline
variable & $\hat{\beta}$ & Std. Error & p-value \\ \hline
intercept & -0.00 & 0.26 & 0.99 \\ \hline
$36 < age < 55$ & $0.42$ & $0.07$ & $6.06e^{-9}$ \\ \hline
$56 < age < 75$ & $0.37$ & $0.07$ & $8.91e^{-7}$ \\ \hline
$age > 76$ & $0.62$ & $0.18$ & $0.00$ \\ \hline
Asian or Pacific Islander & $ -0.75 $ & $0.27$ & $0.01$ \\ \hline
black & $-1.89$ & $0.26$ & $1.25e^{-12}$ \\ \hline
nec & $-0.75$ & $0.26$ & $0.01$ \\ \hline
white & $0.09$ & $0.24$ & $0.68$ \\ \hline
$income > 150k$ & $0.14$ & $0.11$ & $0.22$ \\ \hline
$income < 25k$ & $-0.38$ & $0.10$ & $0.01$ \\ \hline
$25k < income < 50k$ & $-0.27$ & $0.10$ & $0.01$ \\ \hline
$50k < income < 75k$ & $-0.19$ & $0.10$ & $0.06$ \\ \hline
$75k < income < 100k$ & $-0.31$ & $0.11$ & $0.01$ \\ \hline
\end{tabular}
\end{center}

@@

```{r}
#prediction with posterior_linpred()
posterior_prob <- posterior_linpred(mod, transform = TRUE, newdata = post_strat_cellcount_2)
poststrat_prob <- posterior_prob %*% post_strat_cellcount_2$n / sum(post_strat_cellcount_2$n)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)
```

```{r}
# predictio using predict()
post_strat_cellcount_2$estimate <-
  mod %>%
  predict(newdata = post_strat_cellcount_2)
```

```{r}
# prediction using add_prediction_draw
post_stratified_estimates <-
  mod %>%
  tidybayes::add_predicted_draws(newdata = census_data) %>%
  rename(alp_predict = .prediction) %>%
  mutate(alp_predict_prop = alp_predict*cell_prop_of_division_total) %>%
  group_by(state, .draw) %>%
  summarise(alp_predict = sum(alp_predict_prop)) %>%
  group_by(state) %>%
  summarise(mean = mean(alp_predict),
  lower = quantile(alp_predict, 0.025),
  upper = quantile(alp_predict, 0.975))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lme4)
library(merTools)
library(readr)
library(knitr)
```

@@

```{r}
clean_survey_2 <- read_csv("clean-survey-2.csv")
mod <- glmer(binary ~ age_group + (1|education_grouped) + race_ethnicity + household_income_grouped,
           data = clean_survey_2,
           family = binomial()
           )
```

### Summary Table
\begin{center}
\captionof{table}{statistics summary for logistic regression}
\begin{tabular}{|l|l|l|l|}
\hline
variable & $\hat{\beta}$ & Std. Error & p-value \\ \hline
intercept & -0.00 & 0.26 & 0.99 \\ \hline
$36 < age < 55$ & $0.42$ & $0.07$ & $6.06e^{-9}$ \\ \hline
$56 < age < 75$ & $0.37$ & $0.07$ & $8.91e^{-7}$ \\ \hline
$age > 76$ & $0.62$ & $0.18$ & $0.00$ \\ \hline
Asian or Pacific Islander & $ -0.75 $ & $0.27$ & $0.01$ \\ \hline
black & $-1.89$ & $0.26$ & $1.25e^{-12}$ \\ \hline
nec & $-0.75$ & $0.26$ & $0.01$ \\ \hline
white & $0.09$ & $0.24$ & $0.68$ \\ \hline
$income > 150k$ & $0.14$ & $0.11$ & $0.22$ \\ \hline
$income < 25k$ & $-0.38$ & $0.10$ & $0.01$ \\ \hline
$25k < income < 50k$ & $-0.27$ & $0.10$ & $0.01$ \\ \hline
$50k < income < 75k$ & $-0.19$ & $0.10$ & $0.06$ \\ \hline
$75k < income < 100k$ & $-0.31$ & $0.11$ & $0.01$ \\ \hline
\end{tabular}
\end{center}

@@

```{r}
# Read in the csv file for post stratification
post_strat_cellcount_2 <- read_csv("~/STA304/Trump-vs-Biden/outputs/post_strat_cellcount-2.csv")
# get post stratification estimates using predict()
post_strat_cellcount_2$estimate <-
  mod %>%
  predict(newdata = post_strat_cellcount_2, allow.new.level = TRUE, type="response")
```

```{r}
post_strat_cellcount_2 %>%
  mutate(president_predict_prop = estimate*prop) %>%
  group_by(education_grouped) %>%
  summarise(president_predict = sum(president_predict_prop)) %>% 
  as.data.frame() %>% 
  knitr::kable()
```

```{r, fig.cap='95% Prediction Intervals for forcasting the Chances that Donald Trump wins the election'}
PI <- predictInterval(merMod = mod, newdata = post_strat_cellcount_2,                         
                      level = 0.95, n.sims = 1000,                         
                      stat = "median", type= "probability",                      
                      include.resid.var = TRUE)

ggplot(aes(x=1:30, y=fit, ymin=lwr, ymax=upr), data=PI[1:30,]) +   
  geom_point() +   geom_linerange() +   
  labs(x="Index", y="Prediction w/ 95% PI") + 
  theme_bw()
```
